Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-05-19 analysis/preregistration_template.Rmd

---
title: "Ecology and Conservation Modelling Preregistration Template -- DRAFT"
author: "Elise Gould, Megan Good, TBD:workshop collaborators"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  github_document
bibliography: "../data/references.bib"
---

>>>>

---
title: "Ecology and Conservation Modelling Preregistration Template -- DRAFT"
author: "Elise Gould, Megan Good, TBD:workshop collaborators"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document: default
bibliography: ../data/references.bib
---
